Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-17 paper/ms.tex
Probably

We also show the evolution of the surface density profile in Fig.~\ref{fig:surf}
We find that in our simulation the atomic and molecular gas surface density and
the SFR surface density is broadly consistent with the expected values for the
Milky Way \citep{2008AA...487..951K,2022ApJ...929L..18E}. The discrepancy between
$1$ and $4\,\textrm{kpc}$ in the molecular and SFR surface density is likely due
to the fact that the distances to molecular clouds which underlines this work
used a simple kinematic distance based on an axisymmetric model of the Milky
Way \citep{2017ApJ...834...57M}, which is not accurate in the bar region where gas
has large non-circular velocities.

>>>>

We also show the evolution of the surface density profile in Fig.~\ref{fig:surf}
We find that in our simulation the atomic and molecular gas surface density and
the SFR surface density is broadly consistent with the expected values for the
Milky Way \citep{2008AA...487..951K,2022ApJ...929L..18E}. The discrepancy between
$1$ and $4\,\textrm{kpc}$ in the molecular and SFR surface density is {\bf probably} due
to the fact that the distances to molecular clouds which underlines this work
used a simple kinematic distance based on an axisymmetric model of the Milky
Way \citep{2017ApJ...834...57M}, which is not accurate in the bar region where gas
has large non-circular velocities.
